(Working Title) Stellar and Planetary Properties of \KT\ \Ci\ Candidates and Confirmation of $N$ Systems, (Including a Planet Receiving Earth-like Insolation?)

### 2015-03-05 ms.tex
Updates from ShareLaTeX

Such effects are not uncommon in \kep\ data. 
\citet{Batalha13} found $\sim 25$ planet candidates to be false positives based on matching
ephemerides between candidates. 
In that paper, the authors limited their search to candidates within $20\arcsec$ of other
objects of interest. 
\citet{Coughlin14} expanded on this method, identifying 685 KOIs as false positives and 
outlining four physical reasons why these anomalies may occur.
While EPIC 201555883 is likely a false positive, it does not appear that it can neatly be
explained by any one of the effects described by \citet{Coughlin14} alone. 
This artifact should be carefully studied in the future, as it may help illuminate other 
potential detector artifacts, both in \kep\ and \KT\ data.

@@

Something about Multis and TTVs will go in here.

@@

>>>>

False positives induced by the presence of a true astrophysical object with the same 
transit ephemeris are not uncommon in \kep\ data. 
\citet{Batalha13} found $\sim 25$ planet candidates to be false positives based on matching
ephemerides between candidates. 
In that paper, the authors limited their search to candidates within $20\arcsec$ of other
objects of interest. 
\citet{Coughlin14} expanded on this method, identifying 685 KOIs as false positives and 
outlining four physical reasons why these anomalies may occur.
While EPIC 201555883 is likely a false positive, it does not appear that it can neatly be
explained by any one of the effects described by \citet{Coughlin14} alone. 
This artifact should be carefully studied in the future, as it may help illuminate other 
potential detector artifacts, both in \kep\ and \KT\ data.

@@

We have presented stellar parameters for all planet candidates systems observed by 
\paperit, confirming \btmtodo{Nconfirm} of the 36 candidates as bona fide planets and 
\btmtodo{NFP} as bona fide false positives.

With the exception of one object, all of the stellar parameters are derived from comparing 
photometric observations to the Dartmouth stellar evolution models. 
As a result, both the stellar and planet parameters are subject to systematic biases induced
by discrepancies between the models and reality.

@@

D.F.M. and D.W.H. were partially supported by the National Science Foundation 
(grant IIS-1124794), the National Aeronautics and Space Administration (grant 
NNX12AI50G), and the Moore–Sloan Data Science Environment at NYU.
